parameters

### 2020-01-20 manuscript/manuscript.Rmd
Fixed table combinations, put into latex format

# combinations table
combins <- expand.grid(params)

#combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"

combins <- combins %>%
  #filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
  arrange(model, feature_extraction )

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[droprows, ]
```

@@

```{r}
kable(tab, format  = "pandoc")
```

This leads to  `r nrow(combins)` combinations of configurations:

```{r}
kable(combins, row.names = TRUE, format = "pandoc")
```

>>>>

# combinations table
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
```

@@

```{r}
kable(tab, "latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```

This leads to  `r nrow(combins)` combinations of configurations.

- Naive bayes only goes with tfidf feature extraction.
- For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
- This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.

```{r}
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  footnote(general = "nb model only works with tfidf feature extraction strategy. " )
```
